Proof No Diamond (3 layers)

### 2025-12-11 CAV2026B_cart_pole/CAV2026_a_proof.tex
update the proof

\begin{lemma}
	$B_\delta(R(I))\subseteq R_\delta(I)$.
\end{lemma}

@@

\begin{lemma}
	There exists a polytopes decompose of $X=\bigcup_{Q_i\in \mathcal{Q}} Q_i$ (they may include or exclude their boundaries) and Lipschitz continuous functions $f_i$ assigned for each polytopes that can define $p$:\begin{align*}
		p(x) = f_i(x)\quad \text{if }x\in Q_i
	\end{align*}
\end{lemma}

@@

\begin{lemma}
	For each $Q_i$, there exists $\varepsilon >0$ such that $R(I)\cap Q_i$ is attractive in the region $B_\varepsilon(R(I)\cap Q_i)\cap Q_i$.
\end{lemma}

\begin{proof}
	In this proof, we use $R_i$ to denote $R(I)\cap Q_i$.
\end{proof}

>>>>

\begin{lemma}
	$B_{\delta/2}(R_{\delta/2}(I))\subseteq R_\delta(I)$.
\end{lemma}

@@

\begin{lemma}
	There exists a finite polytopes decompose of $X=\bigcup_{i\in I,\ I\text{ is finite}} Q_i$ (they may include or exclude their boundaries) and Lipschitz continuous functions $f_i$ assigned for each polytopes that can define $p$:\begin{align*}
		p(x) = f_i(x)\quad \text{if }x\in Q_i
	\end{align*}
\end{lemma}

@@

\begin{lemma}
	There exists $\varepsilon >0$ such that $R_{\delta/2}(I)$ is attractive in the region $\bigcup_{i\in I}B_\varepsilon(R_{\delta/2}(I)\cap Q_i)\cap Q_i$.
\end{lemma}

\begin{proof}
	In this proof, we use $R_i$ to denote each $R_{\delta/2}(I)\cap Q_i$. We need to show $R_{\delta/2}(I)$ is attractive in $\bigcup_{i\in I}B_\varepsilon(R_i)\cap Q_i$.

	By assumption and definition, each $Q_i$ is assigned with a Lipschitz continuous function $f_i$ with Lipschitz constant $K_i$. Let $K = \max_{i\in I} K_i$ and $\varepsilon = \frac{\delta}{2K+1}$.

	For a point $y$ in $B_\varepsilon(R_i)\cap Q_i$, there exists $x\in R_i$ such that $d(x,y)<\varepsilon$. We consider $succ_p(y)$ and $succ_p(x)$.

	Since $x,y\in Q_i$, $d(p(x),p(y))\leq K_i d(x,y) < K \varepsilon<\delta/2$. Because $x\in R_i\subseteq R_{\delta/2}(I)$, by definition, since $succ_p(y)\in B_{K_i\varepsilon}(succ_p(x))$ and $x\in R_{\delta/2}(I)$, then $succ_p(y)\in R_{\delta/2}(I)$.

	This is what we want to show.
\end{proof}

\begin{lemma}
	There is a region $A$ satisfying the following:
	\begin{itemize}
			\item A is a union of polytopes.
		\item $A\supseteq R_{\delta/2}(I)$
		\item $A\subseteq\bigcup_{i\in I}B_\varepsilon(R_{\delta/2}(I)\cap Q_i)\cap Q_i$
	\end{itemize}
	Hence, from $A$ we can construct a DT certificate.
\end{lemma}
